Table compiler

### 2017-12-06 analyses/05-table-compiler.Rmd
Add data reference line

```{r}
## Column names
rownames <- c("Group", "# taxa", "# characters", "Age range (MYA)", "Mass extinction (MYA)", "Reference(s)")

@@

## References (to be filled in LaTeX)
reference <- rep("", length(slugs))

## Formatting the table
table_out <- data.frame(group, ntaxa, mcharacters, age_ranges, mass, reference)
table_out <- t(table_out)
colnames(table_out) <- dataset
rownames(table_out) <- rownames

@@

sink(file = "../manuscript/tables/datasets.tex")
xtable(table_out, caption = table_caption)
sink()
```

>>>>

```{r}
## variable names
rownames <- c("Group", "# taxa", "# characters", "Age range (MYA)", "Mass extinction (MYA)", "Reference", "Data reference")

@@

## References (to be filled in LaTeX)
reference <- rep("", length(slugs))
dataref <- rep("", length(slugs))

## Formatting the table
table_out <- data.frame(group, ntaxa, mcharacters, age_ranges, mass, reference, dataref)
table_out <- t(table_out)
colnames(table_out) <- dataset
rownames(table_out) <- rownames

@@

sink(file = "../manuscript/tables/raw_datasets.tex")
xtable(table_out, caption = table_caption)
sink()
```
